Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 6
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{The focus was on the method to validate PV systems projects, based on formal methods that can cover the design-space better than simulation tools. 
We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2 GB when compared to 9.2 GB of CBMC and 19.2 GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.

>>>>

\textcolor{red}{Our main focus was on the method to validate PV system projects, based on software model checking, which can cover the design-space better than simulation tools. 
We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The experimental results from automated verification and simulation tools were compared with information collected from dwelles of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2 GB when compared to 9.2 GB of CBMC and 19.2 GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
